---
title: "R Cheat Sheet"
author: "Kathrine McAulay"
format: gfm
editor: visual
---

## Things I always forget

### Updating GitHub authentication




### Negating %in%

There isn't a built-in way to do this; could assign `Negate('%in%')` to anything, but `%!in%` seems logical

```{r}
`%!in%` = Negate(`%in%`)
```

Source: [Stack Overflow](https://stackoverflow.com/questions/38351820/negation-of-in-in-r), additional similar solutions here and in linked post.


### Excluding geom_boxplot outliers

If overlaying `geom_jitter` and `geom_boxplot`, points representing outliers will be plotted with both geoms; exclude these from `geom_boxplot` using `outlier.shape = NA`, for example:

```{r}
library(ggplot2)
iris |>
  ggplot(aes(x = Species, y = Sepal.Width)) +
  geom_boxplot() +
  geom_jitter(aes(color = Species))

iris |>
  ggplot(aes(x = Species, y = Sepal.Width)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(aes(color = Species))
  
```

### Pivoting data

Pass additional arguements in `values_fun` when using `pivot_wider`with the following format: `values_fn = function(x){mean(x,na.rm = T)}`

```{r}
library(dplyr)
library(tidyr)
iris |>
  select(Sepal.Length, Species) |>
  pivot_wider(names_from = Species,
              values_from = Sepal.Length,
              values_fn = function(x){mean(x,na.rm = T)})
```

Source: [pivot_wider documentation](http://127.0.0.1:63596/help/library/tidyr/html/pivot_wider.html) and [this GitHub issue](https://github.com/tidyverse/tidyr/issues/1114)
